A Survey Wearable Device Risk Perceptions

### 2015-01-05 wearables_survey.tex
Redid Related Work: smartphones, risk perceptions.

\subsection{Smartphones and Wearables Concerns}
{\color{red} Add way more details about Felt's study, so that it's clear how we borrowed the methodology, without the reader having to read that paper.}
There exists work which addresses anticipated privacy and security challenges related to mobile and wearable devices from a system standpoint, such as \cite{DiPietro}. However, works like these are not grounded in user research to make claims to the most relevant concerns for the average user. Felt et. al's study of smartphone user concerns \cite{Felt} was the first to investigate the security and privacy research landscape from a user study standpoint. The survey asked 3,115 smartphone users about 99 risks associated with various smartphone privileges. Our work is motivated by this mobile study, and aims to also investigate wearables security and privacy with a user focus to find the most relevant challenges. To our knowledge, our work is the first of its kind to investigate user concerns for wearable devices.

\subsection{Technology Risk Perceptions}
{\color{red} Again, you need to add lots more about this paper, so that it's clear from your description what they did, and how we build upon it.}
While evaluating which are the most pressing concerns for users, it is also important to take into account how users' perception of particular technology. A seminal risk-benefit analysis psychometric study by Fischoff \cite{Fischhoff} studied how 76 users perceived the risks and benefits of 30 activities and technologies. In our survey, we also explore how risk and benefit perception plays a role in how users perceive various new devices and new technologies in wearables.

{\color{red} You really need to cite ~\cite{Denning2014} in this section.}

{\color{red} To make it flow, add 1-3 sentences here about the gaps in the related work, which then motivates our study (e.g., while people have looked at X, we are aware of no work that has looked at Y. Thus, we performed a survey to examine Y).}

@@

\subsection{Analysis}
After removing 465 incomplete responses, our sample consisted of 1,785 participants. Of these X, A\% were male, with a median age of B. For the wearables and smartphone questions, we use the very upset rate (VUR) of various scenarios, rather than taking an average of the participants' upset ratings (after assigning each rating a number) from the likert scale. The VUR also does not presume that the ratings, ranging from indifferent to very upset, are linearly spaced. Additionally, we believe that everyone would be upset at least a little bit at the given scenarios, in which an device takes action without permission. Therefore, we believe that the main distinguishing factor of a participant reacting to a given situation is if they are maximally upset or not, rather than how upset they were. Although participants gave a wide range of numbers (i.e. a participant who answered that one technology was six orders of magnitude more beneficial than another), we do not normalize the numerical responses for the risk/benefit analysis. Rather, we use values such as the median, and various quartiles for our analysis which are not heavily impacted by outliers. Two researchers independently coded 1,785 open-ended responses and had an initial agreement rate of 89.78\%. The researchers discussed any disagreements, and resolved them so that the final codings reflect unanimous agreement.

>>>>

\subsection{Smartphones and Wearables Concerns}
There exists work which addresses anticipated privacy and security challenges related to mobile and wearable devices from a system standpoint, such as \cite{DiPietro}. However, works like these are not grounded in user research and do not make claims about what the the most relevant concerns for the average user are. Felt et. al's study of smartphone user concerns \cite{Felt} was the first to investigate the smartphone security and privacy landscape from a user study standpoint. The survey asked 3,115 smartphone users about 99 risks associated with various smartphone privileges. Participants were asked how upset they would be if a certain action had occurred without their permission. Participants rated each situation on a likert scale ranging from indifferent (1) to very upset (5). Our work is motivated by this mobile study, and aims to also investigate wearables security and privacy with a user focus to find the most relevant challenges. We use a similar scale to ask our users how upset they would be if a certain action was taken without their permission, but ask questions about new capabilities on wearable devices. To our knowledge, our work is the first of its kind to investigate such user concerns.

\subsection{Technology Risk Perceptions}
While evaluating which are the most pressing concerns for users, it is also important to take into account how users' perception of particular technology. A seminal risk-benefit analysis psychometric study by Fischoff \cite{Fischhoff} studied how 76 users perceived the risks and benefits of 30 activities and technologies. In the study, participants were prompted to rate the risks and benefits of 30 activities and technologies for all people affected by the technology, for a long period of time. The participants rated these technologies with respect to each other on a numerical scale, being instructed to rate the least risky or least beneficial technology a 10 and scaling the ratings linearly (i.e. a technology with risk rating 20 would be considered twice as risky compared to a technology with a risk rating of 10). In our survey, we use a similar prompt to ask participants to rate the risks and benefits of 20 new technologies. Denning et. al conducted a study investigating privacy perspectives the bystanders of wearable devices ~\cite{Denning2014}. Bystanders expressed concerns due to the subtle, easy-to-use, and prevalent nature of wearables. While people have conducted studies on privacy concerns with respect to wearables, we are aware of no work which as looked at privacy perspectives of the owner of the device. In our survey, we show how risk and benefit perception plays a role in how users perceive various new devices and new technologies in wearables.

@@

\subsection{Analysis}
After removing 465 incomplete responses, our sample consisted of 1,785 participants. Of these X, 57.87\% were male, with a median age of 29 (sigma = 10.37). For the wearables and smartphone questions, we use the very upset rate (VUR) of various scenarios, rather than taking an average of the participants' upset ratings (after assigning each rating a number) from the likert scale. The VUR also does not presume that the ratings, ranging from indifferent to very upset, are linearly spaced. Additionally, we believe that everyone would be upset at least a little bit at the given scenarios, in which an device takes action without permission. Therefore, we believe that the main distinguishing factor of a participant reacting to a given situation is if they are maximally upset or not, rather than how upset they were. Although participants gave a wide range of numbers (i.e. a participant who answered that one technology was six orders of magnitude more beneficial than another), we do not normalize the numerical responses for the risk/benefit analysis. Rather, we use values such as the median, and various quartiles for our analysis which are not heavily impacted by outliers. Two researchers independently coded 1,785 open-ended responses and had an initial agreement rate of 89.78\%. The researchers discussed any disagreements, and resolved them so that the final codings reflect unanimous agreement.
